<<<<<<< HEAD
---
title: "Interactive AR Code"
author: ""
date: "April, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Credit
Based on Andrew Brooks' work, http://brooksandrew.github.io/simpleblog/articles/association-rules-explore-app/

## Library
```{r library, echo=T, message=FALSE, warning=FALSE, results='hide'}
library('Rsenal') # Rsenal is a R package developed by Andrew Brooks with several science tools
library('devtools') # collection of package development tools
library('shiny') # R interactive web app
library('arules') # to perform mining association rules and frequent item sets
library('arulesViz') # to visualize arules result
```

## Load data
```{r loadData}
data <- read.csv2(
  "test2.csv", # data file location
  sep = "," # separate each variable based on ,
)
```


## Rshiny App
```{r arApp}
arApp <- function (dataset,
                   # input data set
                   bin = T,
                   # returns the binary representation of input data set
                   vars = 5,
                   # default variables
                   supp = 0.1,
                   # default support values, item's frequency of occurrence
                   conf = 0.5) {
                   # default conditional probability
  
  # ## binning numeric data
  for (i in 1:ncol(dataset)) {
    if (class(dataset[, i]) %in% c('numeric', 'integer'))
      dataset[, i] <- Rsenal::depthbin(dataset[, i], nbins = 10)
  }
  
  
  #####################################################################################################
  ## calling Shiny App
  shinyApp(
    ui = shinyUI(pageWithSidebar(
      headerPanel("AR for TechPolicy"), # header of the app
      
      sidebarPanel( # side panel for the app
        conditionalPanel(condition = "input.samp=='Sample'", # load the variables on to the side panel
                         numericInput("nrule", 'Number of Rules', 5), br()),
                         # default number of rules 
        
        conditionalPanel(
          condition = "input.mytab=='graph'",
          radioButtons(
            'graphType',
            label = 'Graph Type',
            choices = c('itemsets', 'items'),
            inline = T
          ),
          br()
        ),
        
        conditionalPanel(condition = "input.lhsv=='Subset'",
                         uiOutput("choose_lhs"), br()),
        
        conditionalPanel(condition = "input.rhsv=='Subset'",
                         uiOutput("choose_rhs"), br()),
        
        conditionalPanel(
          condition = "input.mytab=='grouped'",
          sliderInput(
            'k',
            label = 'Choose # of rule clusters',
            min = 1,
            max = 150,
            step = 1,
            value = 15
          ),
          br()
        ),
        
        conditionalPanel(
          condition = "input.mytab %in%' c('grouped', 'graph', 'table', 'datatable', 'scatter', 'paracoord', 'matrix', 'itemFreq')",
          radioButtons(
            'samp',
            label = 'Sample',
            choices = c('All Rules', 'Sample'),
            inline = T
          ),
          br(),
          uiOutput("choose_columns"),
          br(),
          sliderInput(
            "supp",
            "Support:",
            min = 0,
            max = 1,
            value = supp ,
            step = 1 / 10000
          ),
          br(),
          sliderInput(
            "conf",
            "Confidence:",
            min = 0,
            max = 1,
            value = conf ,
            step = 1 / 10000
          ),
          br(),
          selectInput(
            'sort',
            label = 'Sorting Criteria:',
            choices = c('lift', 'confidence', 'support')
          ),
          br(),
          br(),
          numericInput("minL", "Min. items per set:", 2, min = 2),
          br(),
          numericInput("maxL", "Max. items per set::", 3, min = 2),
          br(),
          radioButtons(
            'lhsv',
            label = 'LHS variables',
            choices = c('All', 'Subset')
          ),
          br(),
          radioButtons(
            'rhsv',
            label = 'RHS variables',
            choices = c('All', 'Subset')
          ),
          br(),
          downloadButton('downloadData', 'Download Rules as CSV')
        )
        
      ),
      
      mainPanel(
        a("credits in code"),
        tabsetPanel(
          id = 'mytab',
          tabPanel(
            'Grouped',
            value = 'grouped',
            plotOutput("groupedPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Graph',
            value = 'graph',
            plotOutput("graphPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Scatter',
            value = 'scatter',
            plotOutput("scatterPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Parallel Coordinates',
            value = 'paracoord',
            plotOutput("paracoordPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Matrix',
            value = 'matrix',
            plotOutput("matrixPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'ItemFreq',
            value = 'itemFreq',
            plotOutput("itemFreqPlot", width = '100%', height = '100%')
          ),
          tabPanel('Table', value = 'table', verbatimTextOutput("rulesTable")),
          tabPanel('Data Table', value = 'datatable', dataTableOutput("rulesDataTable"))
        )
      )
      
    )),
    
    
    
    ###################################################################################################
    server = function(input, output) {
      output$choose_columns <- renderUI({
        checkboxGroupInput(
          "cols",
          "Choose variables:",
          choices  = colnames(dataset),
          selected = colnames(dataset)[1:vars]
        )
      })
      
      
      output$choose_lhs <- renderUI({
        checkboxGroupInput(
          "colsLHS",
          "Choose LHS variables:",
          choices  = input$cols,
          selected = input$cols[1]
        )
      })
      
      output$choose_rhs <- renderUI({
        checkboxGroupInput(
          "colsRHS",
          "Choose RHS variables:",
          choices  = input$cols,
          selected = input$cols[1]
        )
      })
      
      ## Extracting and Defining arules
      rules <- reactive({
        tr <- as(dataset[, input$cols], 'transactions')
        arAll <-
          apriori(
            tr,
            parameter = list(
              support = input$supp,
              confidence = input$conf,
              minlen = input$minL,
              maxlen = input$maxL
            )
          )
        
        if (input$rhsv == 'Subset' & input$lhsv != 'Subset') {
          varsR <- character()
          for (i in 1:length(input$colsRHS)) {
            tmp <-
              with(dataset, paste(input$colsRHS[i], '=', levels(as.factor(
                get(input$colsRHS[i])
              )), sep = ''))
            varsR <- c(varsR, tmp)
          }
          ar <- subset(arAll, subset = rhs %in% varsR)
          
        } else if (input$lhsv == 'Subset' &
                   input$rhsv != 'Subset') {
          varsL <- character()
          for (i in 1:length(input$colsLHS)) {
            tmp <-
              with(dataset, paste(input$colsLHS[i], '=', levels(as.factor(
                get(input$colsLHS[i])
              )), sep = ''))
            varsL <- c(varsL, tmp)
          }
          ar <- subset(arAll, subset = lhs %in% varsL)
          
        } else if (input$lhsv == 'Subset' &
                   input$rhsv == 'Subset') {
          varsL <- character()
          for (i in 1:length(input$colsLHS)) {
            tmp <-
              with(dataset, paste(input$colsLHS[i], '=', levels(as.factor(
                get(input$colsLHS[i])
              )), sep = ''))
            varsL <- c(varsL, tmp)
          }
          varsR <- character()
          for (i in 1:length(input$colsRHS)) {
            tmp <-
              with(dataset, paste(input$colsRHS[i], '=', levels(as.factor(
                get(input$colsRHS[i])
              )), sep = ''))
            varsR <- c(varsR, tmp)
          }
          ar <-
            subset(arAll, subset = lhs %in% varsL & rhs %in% varsR)
          
        } else {
          ar <- arAll
        }
        quality(ar)$conviction <-
          interestMeasure(ar, method = 'conviction', transactions = tr)
        quality(ar)$hyperConfidence <-
          interestMeasure(ar, method = 'hyperConfidence', transactions = tr)
        quality(ar)$cosine <-
          interestMeasure(ar, method = 'cosine', transactions = tr)
        quality(ar)$chiSquare <-
          interestMeasure(ar, method = 'chiSquare', transactions = tr)
        quality(ar)$coverage <-
          interestMeasure(ar, method = 'coverage', transactions = tr)
        quality(ar)$doc <-
          interestMeasure(ar, method = 'doc', transactions = tr)
        quality(ar)$gini <-
          interestMeasure(ar, method = 'gini', transactions = tr)
        quality(ar)$hyperLift <-
          interestMeasure(ar, method = 'hyperLift', transactions = tr)
        ar
      })
      
      # Rule length
      nR <- reactive({
        nRule <-
          ifelse(input$samp == 'All Rules', length(rules()), input$nrule)
      })
      
      ## Grouped Plot #########################
      output$groupedPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()],
             method = 'grouped',
             control = list(k = input$k))
      }, height = 800, width = 800)
      
      ## Graph Plot ##########################
      output$graphPlot <- renderPlot({
        ar <- rules()
        plot(
          sort(ar, by = input$sort)[1:nR()],
          method = 'graph',
          control = list(type = input$graphType)
        )
      }, height = 800, width = 800)
      
      ## Scatter Plot ##########################
      output$scatterPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()], method = 'scatterplot')
      }, height = 800, width = 800)
      
      ## Parallel Coordinates Plot ###################
      output$paracoordPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()], method = 'paracoord')
      }, height = 800, width = 800)
      
      ## Matrix Plot ###################
      output$matrixPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()],
             method = 'matrix')
      }, height = 800, width = 800)
      
      ## Item Frequency Plot ##########################
      output$itemFreqPlot <- renderPlot({
        trans <- as(dataset[, input$cols], 'transactions')
        itemFrequencyPlot(trans)
      }, height = 800, width = 800)
      
      ## Rules Data Table ##########################
      output$rulesDataTable <- renderDataTable({
        ar <- rules()
        rulesdt <- rules2df(ar)
        rulesdt
      })
      
      ## Rules Printed ########################
      output$rulesTable <- renderPrint({
        ar <- rules()
        inspect(sort(ar, by = input$sort))
      })
      
      ## Download data to csv ########################
      output$downloadData <- downloadHandler(
        # file download
        filename = 'GoC_PA_AR.csv',
        # string of the filename with extension, csv style
        content = function(file) {
          # takes file path of a nonexistent temp file and writes content to that path
          write.csv(rules2df(rules()), file) # write the file as csv
        }
      )
      
      
    }
  )
}
```

## Run the app
Run all the chunks above and execute the following code.
```{r runARapp, eval = FALSE}
arApp(data)
```

=======
---
title: "Interactive AR Code"
author: ""
date: "April, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Credit
Based on Andrew Brooks' work, http://brooksandrew.github.io/simpleblog/articles/association-rules-explore-app/

## Library
```{r library, echo=T, message=FALSE, warning=FALSE, results='hide'}
library('Rsenal') # Rsenal is a R package developed by Andrew Brooks with several science tools
library('devtools') # collection of package development tools
library('shiny') # R interactive web app
library('arules') # to perform mining association rules and frequent item sets
library('arulesViz') # to visualize arules result
```

## Load data
```{r loadData}
data <- read.csv2(
  "test2.csv", # data file location
  sep = "," # separate each variable based on ,
)
```


## Rshiny App
```{r arApp}
arApp <- function (dataset,
                   # input data set
                   bin = T,
                   # returns the binary representation of input data set
                   vars = 5,
                   # default variables
                   supp = 0.1,
                   # default support values, item's frequency of occurrence
                   conf = 0.5) {
                   # default conditional probability
  
  # ## binning numeric data
  for (i in 1:ncol(dataset)) {
    if (class(dataset[, i]) %in% c('numeric', 'integer'))
      dataset[, i] <- Rsenal::depthbin(dataset[, i], nbins = 10)
  }
  
  
  #####################################################################################################
  ## calling Shiny App
  shinyApp(
    ui = shinyUI(pageWithSidebar(
      headerPanel("AR for TechPolicy"), # header of the app
      
      sidebarPanel( # side panel for the app
        conditionalPanel(condition = "input.samp=='Sample'", # load the variables on to the side panel
                         numericInput("nrule", 'Number of Rules', 5), br()),
                         # default number of rules 
        
        conditionalPanel(
          condition = "input.mytab=='graph'",
          radioButtons(
            'graphType',
            label = 'Graph Type',
            choices = c('itemsets', 'items'),
            inline = T
          ),
          br()
        ),
        
        conditionalPanel(condition = "input.lhsv=='Subset'",
                         uiOutput("choose_lhs"), br()),
        
        conditionalPanel(condition = "input.rhsv=='Subset'",
                         uiOutput("choose_rhs"), br()),
        
        conditionalPanel(
          condition = "input.mytab=='grouped'",
          sliderInput(
            'k',
            label = 'Choose # of rule clusters',
            min = 1,
            max = 150,
            step = 1,
            value = 15
          ),
          br()
        ),
        
        conditionalPanel(
          condition = "input.mytab %in%' c('grouped', 'graph', 'table', 'datatable', 'scatter', 'paracoord', 'matrix', 'itemFreq')",
          radioButtons(
            'samp',
            label = 'Sample',
            choices = c('All Rules', 'Sample'),
            inline = T
          ),
          br(),
          uiOutput("choose_columns"),
          br(),
          sliderInput(
            "supp",
            "Support:",
            min = 0,
            max = 1,
            value = supp ,
            step = 1 / 10000
          ),
          br(),
          sliderInput(
            "conf",
            "Confidence:",
            min = 0,
            max = 1,
            value = conf ,
            step = 1 / 10000
          ),
          br(),
          selectInput(
            'sort',
            label = 'Sorting Criteria:',
            choices = c('lift', 'confidence', 'support')
          ),
          br(),
          br(),
          numericInput("minL", "Min. items per set:", 2, min = 2),
          br(),
          numericInput("maxL", "Max. items per set::", 3, min = 2),
          br(),
          radioButtons(
            'lhsv',
            label = 'LHS variables',
            choices = c('All', 'Subset')
          ),
          br(),
          radioButtons(
            'rhsv',
            label = 'RHS variables',
            choices = c('All', 'Subset')
          ),
          br(),
          downloadButton('downloadData', 'Download Rules as CSV')
        )
        
      ),
      
      mainPanel(
        a("credits in code"),
        tabsetPanel(
          id = 'mytab',
          tabPanel(
            'Grouped',
            value = 'grouped',
            plotOutput("groupedPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Graph',
            value = 'graph',
            plotOutput("graphPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Scatter',
            value = 'scatter',
            plotOutput("scatterPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Parallel Coordinates',
            value = 'paracoord',
            plotOutput("paracoordPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'Matrix',
            value = 'matrix',
            plotOutput("matrixPlot", width = '100%', height = '100%')
          ),
          tabPanel(
            'ItemFreq',
            value = 'itemFreq',
            plotOutput("itemFreqPlot", width = '100%', height = '100%')
          ),
          tabPanel('Table', value = 'table', verbatimTextOutput("rulesTable")),
          tabPanel('Data Table', value = 'datatable', dataTableOutput("rulesDataTable"))
        )
      )
      
    )),
    
    
    
    ###################################################################################################
    server = function(input, output) {
      output$choose_columns <- renderUI({
        checkboxGroupInput(
          "cols",
          "Choose variables:",
          choices  = colnames(dataset),
          selected = colnames(dataset)[1:vars]
        )
      })
      
      
      output$choose_lhs <- renderUI({
        checkboxGroupInput(
          "colsLHS",
          "Choose LHS variables:",
          choices  = input$cols,
          selected = input$cols[1]
        )
      })
      
      output$choose_rhs <- renderUI({
        checkboxGroupInput(
          "colsRHS",
          "Choose RHS variables:",
          choices  = input$cols,
          selected = input$cols[1]
        )
      })
      
      ## Extracting and Defining arules
      rules <- reactive({
        tr <- as(dataset[, input$cols], 'transactions')
        arAll <-
          apriori(
            tr,
            parameter = list(
              support = input$supp,
              confidence = input$conf,
              minlen = input$minL,
              maxlen = input$maxL
            )
          )
        
        if (input$rhsv == 'Subset' & input$lhsv != 'Subset') {
          varsR <- character()
          for (i in 1:length(input$colsRHS)) {
            tmp <-
              with(dataset, paste(input$colsRHS[i], '=', levels(as.factor(
                get(input$colsRHS[i])
              )), sep = ''))
            varsR <- c(varsR, tmp)
          }
          ar <- subset(arAll, subset = rhs %in% varsR)
          
        } else if (input$lhsv == 'Subset' &
                   input$rhsv != 'Subset') {
          varsL <- character()
          for (i in 1:length(input$colsLHS)) {
            tmp <-
              with(dataset, paste(input$colsLHS[i], '=', levels(as.factor(
                get(input$colsLHS[i])
              )), sep = ''))
            varsL <- c(varsL, tmp)
          }
          ar <- subset(arAll, subset = lhs %in% varsL)
          
        } else if (input$lhsv == 'Subset' &
                   input$rhsv == 'Subset') {
          varsL <- character()
          for (i in 1:length(input$colsLHS)) {
            tmp <-
              with(dataset, paste(input$colsLHS[i], '=', levels(as.factor(
                get(input$colsLHS[i])
              )), sep = ''))
            varsL <- c(varsL, tmp)
          }
          varsR <- character()
          for (i in 1:length(input$colsRHS)) {
            tmp <-
              with(dataset, paste(input$colsRHS[i], '=', levels(as.factor(
                get(input$colsRHS[i])
              )), sep = ''))
            varsR <- c(varsR, tmp)
          }
          ar <-
            subset(arAll, subset = lhs %in% varsL & rhs %in% varsR)
          
        } else {
          ar <- arAll
        }
        quality(ar)$conviction <-
          interestMeasure(ar, method = 'conviction', transactions = tr)
        quality(ar)$hyperConfidence <-
          interestMeasure(ar, method = 'hyperConfidence', transactions = tr)
        quality(ar)$cosine <-
          interestMeasure(ar, method = 'cosine', transactions = tr)
        quality(ar)$chiSquare <-
          interestMeasure(ar, method = 'chiSquare', transactions = tr)
        quality(ar)$coverage <-
          interestMeasure(ar, method = 'coverage', transactions = tr)
        quality(ar)$doc <-
          interestMeasure(ar, method = 'doc', transactions = tr)
        quality(ar)$gini <-
          interestMeasure(ar, method = 'gini', transactions = tr)
        quality(ar)$hyperLift <-
          interestMeasure(ar, method = 'hyperLift', transactions = tr)
        ar
      })
      
      # Rule length
      nR <- reactive({
        nRule <-
          ifelse(input$samp == 'All Rules', length(rules()), input$nrule)
      })
      
      ## Grouped Plot #########################
      output$groupedPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()],
             method = 'grouped',
             control = list(k = input$k))
      }, height = 800, width = 800)
      
      ## Graph Plot ##########################
      output$graphPlot <- renderPlot({
        ar <- rules()
        plot(
          sort(ar, by = input$sort)[1:nR()],
          method = 'graph',
          control = list(type = input$graphType)
        )
      }, height = 800, width = 800)
      
      ## Scatter Plot ##########################
      output$scatterPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()], method = 'scatterplot')
      }, height = 800, width = 800)
      
      ## Parallel Coordinates Plot ###################
      output$paracoordPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()], method = 'paracoord')
      }, height = 800, width = 800)
      
      ## Matrix Plot ###################
      output$matrixPlot <- renderPlot({
        ar <- rules()
        plot(sort(ar, by = input$sort)[1:nR()],
             method = 'matrix')
      }, height = 800, width = 800)
      
      ## Item Frequency Plot ##########################
      output$itemFreqPlot <- renderPlot({
        trans <- as(dataset[, input$cols], 'transactions')
        itemFrequencyPlot(trans)
      }, height = 800, width = 800)
      
      ## Rules Data Table ##########################
      output$rulesDataTable <- renderDataTable({
        ar <- rules()
        rulesdt <- rules2df(ar)
        rulesdt
      })
      
      ## Rules Printed ########################
      output$rulesTable <- renderPrint({
        ar <- rules()
        inspect(sort(ar, by = input$sort))
      })
      
      ## Download data to csv ########################
      output$downloadData <- downloadHandler(
        # file download
        filename = 'GoC_PA_AR.csv',
        # string of the filename with extension, csv style
        content = function(file) {
          # takes file path of a nonexistent temp file and writes content to that path
          write.csv(rules2df(rules()), file) # write the file as csv
        }
      )
      
      
    }
  )
}
```

## Run the app
Run all the chunks above and execute the following code.
```{r runARapp, eval = FALSE}
arApp(data)
```

>>>>>>> 1fca9f4696cc664e4e0757b98223cb8427f68d60
